Changes in Patterns of Geometric Sign Groupings as a Model of Social Dynamics Across Aurignacian Phases

### 2025-04-29 endofquarterpaper.qmd
social structure paragraph

>>>>

It is possible that variation in diversity of sign types among sites may be representative of variation in social arrangement or social context. Despite the tendency to conceive of hunter-gatherers as monolithic, previous studies have established a diverse range of hunter-gatherer social arrangements [@Finlayson_Warren_2017; @Riches_1995; @Price_Brown_1985; @Lane_2017]. Ethnographic studies of hunter-gatherers were utilized by @Bloch_1977 to theorize a correlation between the amounts of social structure, instituted hierarchy, and ritual communication in a society. @Conkey_1985 built upon that theorized correlation, arguing that artwork and other forms of material culture can serve as a form of ritual communication, and that an increase in diversity may suggest more elaborate or complex social contexts, specifically in regards to the Paleolithic. It is therefore possible that changes in diversity from site to site, particularly the larger grouping structure of broader versus restricted signs, may be representative of two different types of social arrangment..
